Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-08-04 doc/GMP2015/revision_3/s06_problempinning.tex
Made a talk, consolidated doc/img, began new revision, updated doc todo and .gitignore
Updated paper to say algo is O(V^4). However, I also provide a sketch of what I believe to be a working O(V^3). Updated todo's.

\ClearMyMinHeight
\SetMyMinHeight{.3}{img/silica}
\SetMyMinHeight{.2}{img/Silicon_tetrahedron}

\begin{figure}\centering
    \includegraphics[height=\myMinHeight]{img/Silica}
    \hspace{0.5cm}
    \includegraphics[height=\myMinHeight]{img/Silicon_tetrahedron}
    % \raisebox{0.25\height}{
    %     \includegraphics[height=\myMinHeight]{img/Silicon_tetrahedron}
    % }
    \caption{Example of a single monolayer of a silica (silicon and oxygen) glassy structure. This can be viewed as a triangle-multipin qusecs where the silicon atoms are the triangles and the oxygen atoms are the pins. Not shown here are other monolayers stacked on this one. Each silicon atom has the structure seen to the right, and so binds to another oxygen atom in an adjacent monolayer. Pictures taken from \cite{silica_figure} and \cite{tetra_silica_figure}.}
    \label{fig:silica_glass}
\end{figure}

@@

In all cases, we are specifically interested in how to add additional constraints such that the resulting isostatic structure has a small DR-plan; this way a realization can be found, allowing efficient stress, flex and other property design related to the rigidity matrix. To answer these questions, we first introduce the qusecs' that are used to model these materials. In this section, we discuss Item (2) in detail.

% \begin{figure}\centering
%     (a)
%     \begin{subfigure}{0.2\linewidth}
%         \includegraphics[width=\linewidth]{img/pentl1}
%     \end{subfigure}
%     %
%     $\rightarrow$
%     \begin{subfigure}{0.2\linewidth}
%         \includegraphics[width=\linewidth]{img/pentl2}
%     \end{subfigure}
%     %

%     (b)
%     \begin{subfigure}{0.8\linewidth}
%         \includegraphics[width=\linewidth]{img/pentawesome}
%     \end{subfigure}
%     \caption{Examples of self-similarity via repeated subdivision. In (a), simple subdivision that does not guarantee isostaticity. In (b), a more complicated scheme is used, ensuring that the resulting graph is isostatic but not  tree-decomposable. Credit to \cite{subdivision_paper} for (a).}
%     \label{fig:subdivision}
% \end{figure}

\begin{figure}\centering
    \begin{subfigure}{0.35\linewidth}
        $
        \vcenter{\hbox{\includegraphics[width=.4\linewidth]{img/pentl1}}}
        % \raisebox{-.5\height}{\scalebox{1}{$\rightarrow$}}
        \vcenter{\hbox{$\rightarrow$}}
        \vcenter{\hbox{\includegraphics[width=.4\linewidth]{img/pentl2}}}
        $
        \caption{}\label{fig:subdivision:simple}
    \end{subfigure}
    \begin{subfigure}{0.55\linewidth}
        \includegraphics[width=\linewidth]{img/pentawesome}
        \caption{}\label{fig:subdivision:complicated}
    \end{subfigure}
    \caption{Examples of self-similarity via repeated subdivision. In (\ref{fig:subdivision:simple}) \cite{subdivision_paper}, there is a simple subdivision scheme that does not guarantee isostaticity. In (\ref{fig:subdivision:complicated}), a more complicated scheme is used, ensuring that the resulting graph is isostatic but not  tree-decomposable.}
    \label{fig:subdivision}
\end{figure}

@@

\begin{definition}
    A \dfn{body-hyperpin qusecs} is a constraint system where the objects are rigid bodies,  subsets of which are pinned together by pins; i.e, are incident at a common point.
\end{definition}

@@

\begin{definition}
    A \dfn{triangle-hyperpin graph} is a body-hyperpin graph where each body is a triangle, i.e., it shares  pins with at most 3 other bodies. This is also represented as a hyper-graph where each pin is a vertex and each triangle represents a tri-hyperedge. For such hypergraphs, {\em 1 and 2-dof} can be characterized by $(2,4)$ and $(2,5)$-tightness respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse}.
\end{definition}

@@

\begin{definition}
    A \dfn{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight sub-graph of the parent node or it is trivial. In our case, the trivial nodes are the bodies.
\end{definition}

Provided such $(k,l)$-sparse graphs are matroidal (conditions given in \cite{Lee:2007:PGA}),
the notion of a canonical DR-plan extends directly to the case when the hypergraph is $(k,l)$-sparse (i.e., independent) using the straightforward notion of trivial and non-trivial intersections and $(k,l)$-tightness conditions as in Section \ref{sec:DRP}. In particular, we define canonical DR-plans with similar properties for the 1 and 2-dof body-pin and triangle-hyperpin systems defined above.

\begin{observation*}
\label{obs:bodypin_drp}
For the 1-dof body-pin graphs described above that are $(3,4)$-sparse, a $(3,4)$-tight canonical DR-plan exists where every node of a $(3,4)$-sparse graph satisfies one of the following: (1) its children are 2 proper vertex-maximal 1-dof graphs that intersect on another 1-dof graph; or (2) its children are all of the proper maximal 1-dof sub-graphs, pairwise sharing at most one body.
\end{observation*}

% \begin{observation}
% \label{obs:bodypin_drp}
%     For the 1-dof body-pin graphs described above, $(3,4)$-sparsity corresponds to a canonical DR-plan whose nodes satisfy one of the following, either
%     (a) the children are 2 proper vertex maximal 1-dof graphs that intersect on another 1-dof graph, or
%     (b) the children are a number of proper maximal 1-dof sub-graphs, sharing at most one body.
% \end{observation}

@@

%     For item 2, consider the case where we have more than 2 proper vertex maximal 1-dof sub-graphs $s_1, ..., s_k, k > 2$. Then, if $k_i$ and $k_j$ are joined by $2$ pins, $k_i \cup k_j$ would be $(3,4)$-tight and hence $k_i$ and $k_j$ are not vertex maximal.
% \end{proof}

@@

\ClearMyMinHeight
\SetMyMinHeight{.2}{img/bodypin}
\SetMyMinHeight{.2}{img/epsfromtikz/bodypin_graph}
\SetMyMinHeight{.35}{img/epsfromtikz/bodypin_drp}
\SetMyMinHeight{.2}{img/bodypin2}

\begin{figure*}\centering
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/bodypin}
        \caption{}\label{fig:bodypindrp:a}
    \end{subfigure}
    %
    \hfill
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/bodypin_graph}
        \caption{}\label{fig:bodypindrp:b}
    \end{subfigure}
    %
    \hfill
    \begin{subfigure}{0.35\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/bodypin_drp}
        \caption{}\label{fig:bodypindrp:c}
    \end{subfigure}
    %
    \hfill
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/bodypin2}
        \caption{}\label{fig:bodypindrp:d}
    \end{subfigure}
    %
    \caption{(\ref{fig:bodypindrp:a}) A 1-dof body-pin graph. (\ref{fig:bodypindrp:b}) The corresponding body-bar graph, explained in Definition \ref{def:body-pin}. (\ref{fig:bodypindrp:c}) The 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (\ref{fig:bodypindrp:d}) The result of adding one such body to the bold-faced node.}
    \label{fig:bodypindrp}
    %
\end{figure*}

@@

% \begin{proof}
%     Suppose we are given a body-pin graph and its corresponding body-bar graph $G$ and have obtained the 1-dof DR-plan $T$. Each node of $T$ will then be a vertex maximal proper 1-dof sub-graph of $G$.

%     To make the graph isostatic, we need only add one body and pin it to 2 other bodies. Doing so will cause $G$ to become $(3,3)$-tight. We choose the 2 bodies to pin to by choosing a node $b$ in $T$ and looking at its children. From Observation \ref{rem:1dofcanon}, we know that the children can only be joined by a single pin or a sub-graph. We pin the new body to bodies in two separate children. Doing so will ensure that all children of $b$ will have 1-dof and all ancestors of $b$ (including $b$) will now be isostatic.

@@

\begin{remark}
\label{obs:algebraic_completion}
    While the proof for Theorem \ref{thm:1dofcase} gives us a DR-plan for the isostatic completion with minimum fan-in, (a reasonable measure of algebraic complexity), a more nuanced measure that treats solutions of 1-dof and 2-dof systems as 1 or 2 parameter families would no longer be optimized by the algorithm given in that proof. In particular, the complexity of the standard algorithm in the $k$-dof case would be exponential in $k$ (even if the case were matroidal and an optimal DR-plan is known).
\end{remark}

>>>>

\ClearMyMinHeight
\SetMyMinHeight{.3}{../../img/silica}
\SetMyMinHeight{.2}{../../img/Silicon_tetrahedron}

\begin{figure}\centering
    \includegraphics[height=\myMinHeight]{../../img/Silica}
    \hspace{0.5cm}
    \includegraphics[height=\myMinHeight]{../../img/Silicon_tetrahedron}
    % \raisebox{0.25\height}{
    %     \includegraphics[height=\myMinHeight]{../../img/Silicon_tetrahedron}
    % }
    \caption{Example of a single monolayer of a silica (silicon and oxygen) glassy structure. This can be viewed as a triangle-multipin qusecs where the silicon atoms are the triangles and the oxygen atoms are the pins. Not shown here are other monolayers stacked on this one. Each silicon atom has the structure seen to the right, and so binds to another oxygen atom in an adjacent monolayer. Pictures taken from \cite{silica_figure} and \cite{tetra_silica_figure}.}
    \label{fig:silica_glass}
\end{figure}

@@

In all cases, we are specifically interested in how to add additional constraints such that the resulting isostatic structure has a small DR-plan; this way a realization can be found, allowing efficient stress, flex and other property design related to the rigidity matrix. To answer these questions, we first introduce the qusecs that are used to model these materials. In this section, we discuss Item (2) in detail.

% \begin{figure}\centering
%     (a)
%     \begin{subfigure}{0.2\linewidth}
%         \includegraphics[width=\linewidth]{../../img/pentl1}
%     \end{subfigure}
%     %
%     $\rightarrow$
%     \begin{subfigure}{0.2\linewidth}
%         \includegraphics[width=\linewidth]{../../img/pentl2}
%     \end{subfigure}
%     %

%     (b)
%     \begin{subfigure}{0.8\linewidth}
%         \includegraphics[width=\linewidth]{../../img/pentawesome}
%     \end{subfigure}
%     \caption{Examples of self-similarity via repeated subdivision. In (a), simple subdivision that does not guarantee isostaticity. In (b), a more complicated scheme is used, ensuring that the resulting graph is isostatic but not  tree-decomposable. Credit to \cite{subdivision_paper} for (a).}
%     \label{fig:subdivision}
% \end{figure}

\begin{figure}\centering
    \begin{subfigure}{0.35\linewidth}
        $
        \vcenter{\hbox{\includegraphics[width=.4\linewidth]{../../img/pentl1}}}
        % \raisebox{-.5\height}{\scalebox{1}{$\rightarrow$}}
        \vcenter{\hbox{$\rightarrow$}}
        \vcenter{\hbox{\includegraphics[width=.4\linewidth]{../../img/pentl2}}}
        $
        \caption{}\label{fig:subdivision:simple}
    \end{subfigure}
    \begin{subfigure}{0.55\linewidth}
        \includegraphics[width=\linewidth]{../../img/pentawesome}
        \caption{}\label{fig:subdivision:complicated}
    \end{subfigure}
    \caption{Examples of self-similarity via repeated subdivision. In (\ref{fig:subdivision:simple}) \cite{subdivision_paper}, there is a simple subdivision scheme that does not guarantee isostaticity. In (\ref{fig:subdivision:complicated}), a more complicated scheme is used, ensuring that the resulting graph is isostatic but not  tree-decomposable.}
    \label{fig:subdivision}
\end{figure}

@@

% \begin{definition}
%     A \dfn{body-hyperpin qusecs} is a constraint system where the objects are rigid bodies, subsets of which are pinned together by pins (i.e.\ they are incident at a common point.)
% \end{definition}

\begin{definition}
    A \dfn{body-hyperpin qusecs} is a constraint system where the objects are rigid bodies and the constraints are incidences of object subsets at a common point, i.e.\ a pinning of bodies.
\end{definition}

@@

\begin{definition}
    A \dfn{triangle-hyperpin graph} is a body-hyperpin graph where each body is a triangle, i.e.\ it shares  pins with at most 3 other bodies. This is also represented as a hyper-graph where each pin is a vertex and each triangle represents a tri-hyperedge. For such hypergraphs, {\em 1 and 2-dof} can be characterized by $(2,4)$ and $(2,5)$-tightness respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse}.
\end{definition}

@@

\begin{definition}
    A \dfn{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight subgraph of the parent node or it is trivial. In our case, the trivial nodes are the bodies.
\end{definition}

Provided such $(k,l)$-sparse graphs are matroidal (conditions given in \cite{Lee:2007:PGA}),
the notion of a canonical DR-plan extends directly to the case when the hypergraph is $(k,l)$-sparse (i.e.\ independent) using the straightforward notion of trivial and non-trivial intersections and $(k,l)$-tightness conditions as in Section \ref{sec:DRP}. In particular, we define canonical DR-plans with similar properties for the 1 and 2-dof body-pin and triangle-hyperpin systems defined above.

\begin{observation*}
\label{obs:bodypin_drp}
For the 1-dof body-pin graphs described above that are $(3,4)$-sparse, a $(3,4)$-tight canonical DR-plan exists where every node of a $(3,4)$-sparse graph satisfies one of the following: (1) its children are 2 proper vertex-maximal 1-dof graphs that intersect on another 1-dof graph; or (2) its children are all of the proper maximal 1-dof subgraphs, pairwise sharing at most one body.
\end{observation*}

% \begin{observation}
% \label{obs:bodypin_drp}
%     For the 1-dof body-pin graphs described above, $(3,4)$-sparsity corresponds to a canonical DR-plan whose nodes satisfy one of the following, either
%     (a) the children are 2 proper vertex maximal 1-dof graphs that intersect on another 1-dof graph, or
%     (b) the children are a number of proper maximal 1-dof subgraphs, sharing at most one body.
% \end{observation}

@@

%     For item 2, consider the case where we have more than 2 proper vertex maximal 1-dof subgraphs $s_1, ..., s_k, k > 2$. Then, if $k_i$ and $k_j$ are joined by $2$ pins, $k_i \cup k_j$ would be $(3,4)$-tight and hence $k_i$ and $k_j$ are not vertex maximal.
% \end{proof}

@@

\ClearMyMinHeight
\SetMyMinHeight{.2}{../../img/bodypin}
\SetMyMinHeight{.2}{../../img/epsfromtikz/bodypin_graph}
\SetMyMinHeight{.35}{../../img/epsfromtikz/bodypin_drp}
\SetMyMinHeight{.2}{../../img/bodypin2}

\begin{figure*}\centering
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/bodypin}
        \caption{}\label{fig:bodypindrp:a}
    \end{subfigure}
    %
    \hfill
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/epsfromtikz/bodypin_graph}
        \caption{}\label{fig:bodypindrp:b}
    \end{subfigure}
    %
    \hfill
    \begin{subfigure}{0.35\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/epsfromtikz/bodypin_drp}
        \caption{}\label{fig:bodypindrp:c}
    \end{subfigure}
    %
    \hfill
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{../../img/bodypin2}
        \caption{}\label{fig:bodypindrp:d}
    \end{subfigure}
    %
    \caption{(\ref{fig:bodypindrp:a}) A 1-dof body-pin graph. (\ref{fig:bodypindrp:b}) The corresponding body-bar graph, explained in Definition \ref{def:body-pin}. (\ref{fig:bodypindrp:c}) The 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (\ref{fig:bodypindrp:d}) The result of adding one such body to the bold-faced node.}
    \label{fig:bodypindrp}
    %
\end{figure*}

@@

% \begin{proof}
%     Suppose we are given a body-pin graph and its corresponding body-bar graph $G$ and have obtained the 1-dof DR-plan $T$. Each node of $T$ will then be a vertex maximal proper 1-dof subgraph of $G$.

%     To make the graph isostatic, we need only add one body and pin it to 2 other bodies. Doing so will cause $G$ to become $(3,3)$-tight. We choose the 2 bodies to pin to by choosing a node $b$ in $T$ and looking at its children. From Observation \ref{rem:1dofcanon}, we know that the children can only be joined by a single pin or a subgraph. We pin the new body to bodies in two separate children. Doing so will ensure that all children of $b$ will have 1-dof and all ancestors of $b$ (including $b$) will now be isostatic.

@@

\begin{remark}
\label{obs:algebraic_completion}
    While the proof for Theorem \ref{thm:1dofcase} gives us a DR-plan for the isostatic completion with minimum fan-in (a reasonable measure of algebraic complexity), a more nuanced measure that treats solutions of 1-dof and 2-dof systems as 1 or 2 parameter families would no longer be optimized by the algorithm given in that proof. In particular, the complexity of the standard algorithm in the $k$-dof case would be exponential in $k$ (even if the case were matroidal and an optimal DR-plan is known).
\end{remark}

### 2015-08-04 doc/GMP2015/revision_3/s07_pinnedline.tex
Made a talk, consolidated doc/img, began new revision, updated doc todo and .gitignore
Updated paper to say algo is O(V^4). However, I also provide a sketch of what I believe to be a working O(V^3). Updated todo's.

% \begin{subfigure}{.49\linewidth}
%   \centering
%   \includegraphics[width=.8\linewidth]{img/AFM_Innventia_nanocellulose}
%   \caption{}
%   \label{fig:cellulose}
% \end{subfigure}
% \begin{subfigure}{.49\linewidth}
%   \centering
%   \includegraphics[width=\linewidth]{img/crosslink}
%   \caption{}
%   \label{fig:crosslink}
% \end{subfigure}%
% \caption{(a) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. (b) Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}.}
% \end{figure}

\ClearMyMinHeight
\SetMyMinHeight{.32}{img/AFM_Innventia_nanocellulose}
\SetMyMinHeight{.32}{img/crosslink}
\SetMyMinHeight{.32}{img/pinned}

\begin{figure}\centering%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/AFM_Innventia_nanocellulose}
    \caption{}\label{fig:cellulose}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/crosslink}
    \caption{}\label{fig:crosslink}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/pinned}
    \caption{}
    \label{fig:pinned_line}
\end{subfigure}%
\caption{(\ref{fig:cellulose}) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. \ref{fig:crosslink} Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}. \ref{fig:pinned_line} An isostatic pinned line-incidence graph, representing fibrils and their attachments.}
\end{figure}%

@@

A \dfn{pinned line-incidence system} $(G,\delta)$ is a graph $G=(V,E)$ together with parameters $\delta$ specifying $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$, such that each edge is constrained to lie on a line passing through the corresponding pin, i.e.\ $\delta: E \rightarrow \mathbb{R}^2$.
%
% $G=(V,E, w_V, w_E)$
%%is a \textbf{2-dimensional pinned line-incidence graph},
% has weight functions $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$.
%Additionally, there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
%such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
%for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
%such that $e$ is constrained to lie on a line passing through $x$.
%%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$
%
A pinned line-incidence graph $G$ is rigid if $|E| = 2|V|$ and $|E'| \le 2|V'|$ for every induced subgraph $(V',E')$ \cite{sitharam2014incidence}. Note that no trivial motion exists since the pins have fixed positions on the plane. Euclidean transformations are not factored out. In particular, both a single vertex and a single edge are underconstrained graphs.

@@

% \begin{figure}\centering
%     \includegraphics[width=.7\linewidth]{img/pinned}
%     \caption{An isostatic pinned line-incidence graph.}
%     \label{fig:pinned_line}
% \end{figure}

@@

% \noindent
% \note The recombination problem for  pinned line-incidence systems is trivial. Since the pins are given fixed positions in the plane, the solutions of a isostatic sub-system will automatically be consistent with solutions of the remaining of the system.

\sidenote{The recombination problem for  pinned line-incidence systems is trivial. Since the pins are given fixed positions in the plane, the solutions of a isostatic sub-system will automatically be consistent with solutions of the remaining of the system.}

>>>>

% \begin{subfigure}{.49\linewidth}
%   \centering
%   \includegraphics[width=.8\linewidth]{../../img/AFM_Innventia_nanocellulose}
%   \caption{}
%   \label{fig:cellulose}
% \end{subfigure}
% \begin{subfigure}{.49\linewidth}
%   \centering
%   \includegraphics[width=\linewidth]{../../img/crosslink}
%   \caption{}
%   \label{fig:crosslink}
% \end{subfigure}%
% \caption{(a) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. (b) Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}.}
% \end{figure}

\ClearMyMinHeight
\SetMyMinHeight{.32}{../../img/AFM_Innventia_nanocellulose}
\SetMyMinHeight{.32}{../../img/crosslink}
\SetMyMinHeight{.32}{../../img/pinned}

\begin{figure}\centering%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{../../img/AFM_Innventia_nanocellulose}
    \caption{}\label{fig:cellulose}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{../../img/crosslink}
    \caption{}\label{fig:crosslink}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{../../img/pinned}
    \caption{}
    \label{fig:pinned_line}
\end{subfigure}%
\caption{(\ref{fig:cellulose}) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. \ref{fig:crosslink} Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}. \ref{fig:pinned_line} An isostatic pinned line-incidence graph, representing fibrils and their attachments.}
\end{figure}%

@@

\begin{definition}
    A \dfn{pinned line-incidence system} $(G,\delta)$ is a graph $G=(V,E)$ together with parameters $\delta$ specifying $|E|$ \dfn{pins} with fixed positions in $\mathbb{R}^2$, such that each edge is constrained to lie on a line passing through the corresponding pin, i.e.\ $\delta: E \rightarrow \mathbb{R}^2$.
\end{definition}

%
% $G=(V,E, w_V, w_E)$
%%is a \textbf{2-dimensional pinned line-incidence graph},
% has weight functions $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$.
%Additionally, there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
%such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
%for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
%such that $e$ is constrained to lie on a line passing through $x$.
%%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$
%
A pinned line-incidence graph $G$ is rigid if $|E| = 2|V|$ and $|E'| \le 2|V'|$ for every induced subgraph $(V',E')$ \cite{sitharam2014incidence}. Note that no trivial motion exists since the pins have fixed positions on the plane. Euclidean transformations are not factored out. In particular, both a single vertex and a single edge are underconstrained graphs.

@@

% \begin{figure}\centering
%     \includegraphics[width=.7\linewidth]{../../img/pinned}
%     \caption{An isostatic pinned line-incidence graph.}
%     \label{fig:pinned_line}
% \end{figure}

@@

% \sidenote{
Note that the recombination problem for pinned line-incidence systems is trivial. Since the pins are given fixed positions in the plane, the solutions of an isostatic subsystem will automatically be consistent with the solutions of the other subsystems.
% }

### 2015-08-04 doc/GMP2015/revision_3/s08_conclusion.tex
Updated paper to say algo is O(V^4). However, I also provide a sketch of what I believe to be a working O(V^3). Updated todo's.

We have clarified the main source of complexity for the optimal DR-plan and recombination problems. For the former problem, when there are no overconstraints (as is the case for 2D qusecs whose realizations are many common types of layered materials), we defined a canonical DR-plan and showed that any canonical DR-plan is guaranteed to be optimal, a strong Church-Rosser property. This gives an efficient (\candrpcomplexity) algorithm to find an optimal DR-plan that satisfies other desirable characteristics.

@@

The first set of problems are from Section \ref{sec:DRP}:
\begin{openproblem}
    Is there a more efficient algorithm than \candrpcomplexityv\ to find the canonical DR-plan of isostatic 2D bar-joint graphs?
\end{openproblem}

>>>>

We have clarified the main source of complexity for the optimal DR-plan and recombination problems. For the former problem, when there are no overconstraints (as is the case for 2D qusecs whose realizations are many common types of layered materials), we defined a canonical DR-plan and showed that any canonical DR-plan is guaranteed to be optimal, a strong Church-Rosser property. This gives an efficient (\ComplexityCanDRP) algorithm to find an optimal DR-plan that satisfies other desirable characteristics.

@@

The first set of problems are from Section \ref{sec:DRP}:
\begin{openproblem}
    Is there a more efficient algorithm than \ComplexityCanDRPV\ to find the canonical DR-plan of isostatic 2D bar-joint graphs?
\end{openproblem}
